---
title: "Kaggle Titanic"
output: html_notebook
---


#1 Load Data

```{r, Load Data}
#Load data
setwd("C:\\Users\\E V D S\\OneDrive\\Main\\Public\\Open Project\\Titanic\\Data")
train <- read.csv("train.csv",na.strings=c(""))
test <- read.csv("test.csv")
train.raw <- train
test.raw <- test
```

#2 Describe Data



```{r, Missing Data}
library("Amelia")
missmap(train, legend = TRUE, col = c("wheat", "darkred"))
```
Cabin is missing a lot of data, meaning it won't be as useful. Pclass can give similar information without having to estimate values for Cabin so we will remove Cabin from our scope. Age also has missing data, but it is still fairly intact and we might be able to fill in the data based upon the name titles. Also based on historical evidence we know that there is a good chance age will be a significant predictor of survival.PassengerID is also not very useful to us as it is too unique.

```{r, Removing Cabin and PassengerID}
train <- subset(train,select=c(1,2,3,5,6,7,8,10,12))
```

We also wanted to fix age. A "better" way to predict age would be to create a function that predicts age based upon titles in names. However for the sake of simplicty the mean will be used as the estimator.


```{r, Estimate Age}
train$Age[is.na(train$Age)] <- mean(train$Age,na.rm=T)
levels(train$Age) <- levels(test$Age)
```

Now that our data has been cleaned up we can begin to investigate our model.

```{r}
fit <- rpart(Survived ~ Pclass + Sex + Age + Fare ,
               data=train,
               method="class")
```

```{r, Submit}
Prediction <-  predict(fit, test, type ="class")
submit <- data.frame(PassengerId = test$PassengerId, Survived = Prediction)
write.csv(submit, file = "submit.csv", row.names = FALSE)
```
